\begin{thebibliography}{}
  \bibitem[Beu07]{Beutelspacher}
    \textsc{A. Beutelspacher.}
    \emph{Diskrete Mathematik für Einsteiger. Mit Anwendungen in Technik und Informatik.}
    Vieweg, 2007.
  \bibitem[Co00]{Cook}
    \textsc{S. A. Cook}.
    \emph{The P versus NP Problem}.
    Manuscript prepared for the Clay Mathematics Institute for the Millennium Prize Problems, April 2000.
  \bibitem[DDG99]{antcount}
    \textsc{M. Dorigo, G. Di Caro and L. M. Gambardella}.
    \emph{Ant Algorithms for Discrete Optimization}.
    Artificial Life, Spring 1999, Vol. 5, No. 2, Pages 137-172.
  \bibitem[DS04]{Dorigo}
    \textsc{M. Dorigo and T. Stützle}.
    \emph{Ant Colony Optimization}.
    The \textsc{MIT} Press, 2004.
  \bibitem[GHJV04]{Gamma}
    \textsc{E. Gamma, R. Helm, R. E. Johnson, J. Vlissides}.
    \emph{Entwurfsmuster - Elemente wiederverwendbarer objektorientierter Software}.
    Addison Wesley, München 2004.
  \bibitem[GJ79]{GJ}
    \textsc{M. R. Garey and D. S. Johnson}.
    \emph{Computers and Intractability - A Guide to the Theory of NP-Completeness}.
    Freeman, New York, 1979.
  \bibitem[Ka72]{Karp}
    \textsc{R. M. Karp}.
    \emph{Reducibility Among Combinatorial Problems}.
    In Raymond E. Miller and James W. Thatcher. Complexity of Computer Computations. New York: Plenum. pp. 85–103.
  \bibitem[LLRS85]{TSP}
    \textsc{E. L. Lawler, J. K. Lenstra, A. H. G. Rinnooy Kan, and D. B. Shmoys}.
    \emph{The Traveling Salesman Problem}.
    John Wiley \& Sons, 1985.
  \bibitem[Tu09]{Turau}
    \textsc{V. Turau}.
    \emph{Algorithmische Graphentheorie}.
    Oldenbourg, 2009.
  \bibitem[Sip06]{Sipser}
    \textsc{M. Sipser}.
    \emph{Introduction to the Theory of Computation}.
    Thomson, 2006.
  \bibitem[Tomcat]{tomcat}
    \url{http://tomcat.apache.org/}
  \bibitem[Vaz01]{Vazirani}
    \textsc{V. V. Vazirani}.
    \emph{Approximation Algorithms}.
    Springer, 2001.
  \bibitem[VV86]{VV}
    \textsc{L. G. Valiant and V. V. Vazirani}.
    \emph{NP is as easy as detecting unique solutions}.
    Proceedings of the seventeenth annual ACM symposium on Theory of computing, 1985, S. 458–463.
  \bibitem[Wan06]{Wanka}
    \textsc{R. Wanka}.
    \emph{Approximationsalgorithmen - Eine Einführung}.
    Teubner, 2006.
\end{thebibliography}